---
title: "week9_pdf.Rmd"
author: "Phoebe Hessen"
date: "3/20/2020"
output: pdf_document
---

# **Libraries**
```{r, message = F, include = F}
library(tidyverse)
library(ggplot2)
```
# **Data Import**

Data Cleaning Steps:  

* Import data  
* Create new column with the row-wise mean of columns q1-q5  
* Create new column with the row-wise mean of columns q6-q10  

```{r, message = F}
week9_tbl <- read_csv("../data/week3.csv")
week9_tbl <- week9_tbl %>%
    mutate(meanq1q5 = rowMeans(week9_tbl[5:9])) %>%
    mutate(meanq6q10 = rowMeans(week9_tbl[10:14])) 
```

# **Visualization**
```{r, echo = F}
ggplot(week9_tbl, aes(x = meanq1q5, y = meanq6q10)) +
    geom_jitter() +
    geom_smooth(method = "lm", se = F) +
    labs(x = "Mean of Q1-Q5", y = "Mean of Q6-Q10")
```
This is a scatterplot illustrating the relationship between participants' mean score on questions 1-5 and their mean score on questions 6-10, including the OLS regression line. 

# **Analysis**
```{r}
cortest <- cor.test(week9_tbl$meanq1q5, week9_tbl$meanq6q10)
cortest$estimate
cortest$p.value
```

The correlation was `r round(cor(week9_tbl$meanq1q5, week9_tbl$meanq6q10), digits = 2)` (`r round(cor.test(week9_tbl$meanq1q5, week9_tbl$meanq6q10)$p.value, digits = 2)`), which is not statistically significant. 








